An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
small tweaks

Perhaps the most pressing open direction is simply to apply our framework to prediction problems of interest.
We hope that the discussion in \S~\ref{sec:apply-embedd-fram}, and the detailed examples in subsequent works, serve as useful guidelines for doing so.
A particularly promising domain to apply our framework is structured prediction, where relatively few consistent surrogates are known.
Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses~\cite{nowak2022consistency}.

@@

The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
Their construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.
An arbitrary element of the superprediction set is decomposed into a convex combination of elements of $L(\Sc)$, plus an element of $\reals^\Y_+$.
This convex combination is then thresholded at $1/|\Sc|$, where the link function may output $r\in\R$ if the weight on any $u\in\Sc$ with $\Gamma_u \subseteq \gamma_r$ is at least $1/|\Sc|$.
One can see that this construction does achieve separation, but it is less explicitly aligned with any norm in the surrogate report space.
It would be interesting to further compare the two constructions.

>>>>

Perhaps the most pressing open direction is simply to apply our framework to prediction problems of interest.
We hope that the discussion in \S~\ref{sec:apply-embedd-fram}, and the detailed examples in subsequent works, serve as useful guidelines for doing so.
A particularly promising domain to apply our framework is structured prediction, where relatively few consistent surrogates are known.
Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses~\citep{nowak2022consistency}.

@@

The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
Their construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operates in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.
An arbitrary element of the superprediction set is decomposed into a convex combination of elements of $L(\Sc)$, plus an element of $\reals^\Y_+$.
This convex combination is then thresholded at $1/|\Sc|$, where the link function may output $r\in\R$ if the weight on any $u\in\Sc$ with $\Gamma_u \subseteq \gamma_r$ is at least $1/|\Sc|$.
One can see that this construction does achieve separation, but it is less explicitly aligned with any norm in the surrogate report space.
It would be interesting to further compare the two constructions.
